Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
Escenarios en AWS como lista

\item Scenario C (Figure~\ref{subfig:aws3}), joins both previous ones and a single client, 
using a 1Gb network interconnection has 13 GPUs that can be used as if they were locally installed.
\end{itemize}

>>>>

\item Scenario C (Figure~\ref{subfig:aws3}) joins both scenarios A and B. So a 
single client, using a 1Gb network interconnection, has 13 GPUs that can be used as if they were locally installed.
\end{itemize}
